\section{Init Notes}

\subsection{Global Aim:} Optimizing a large city's taxi service.

\subsection{Detailed Aims:} \begin{enumerate}
\item Simplify passengers' access to the service
\item Guarantee a fair management of taxi queues
\end{enumerate}

\subsection{Domain Details:} \begin{itemize}
\item Requests are made via Web/Mobile App
\item Responses contain Taxi Code and Waiting Time 
\item Taxi drivers publish their availability / confirmation via a Mobile App
\item Queue Algorithm (\textit{Original quote:}) 
\begin{quote}
In	particular,	the	city	is	
divided	in	 taxi	 zones	 (approximately	 2	 km2 each).	 Each	 zone	is	associated	 to	a	
queue	of	taxis.	The	system	automatically	computes	the	distribution	of	taxis	in	the	
various	zones	based	on	 the	GPS	information	it	receives	 from	each	 taxi.	When	a	
taxi	is	available,	its	identifier	is	stored	in	the	queue	of	taxis	in	the	corresponding	
zone.		
When	a	 request	arrives	 from	a	certain	zone,	 the	system	 forwards	it	 to	 the	 first	
taxi	 queuing	 in	 that	 zone.	 If	 the	 taxi	 confirms,	 then	 the	 system	 will	 send	 a	
confirmation	to	the	passenger.	If	not,	then	the	system	will	forward	the	request	to	
the	second	in	the	queue	and	will,	at	the	same	time,	move	the	first	taxi	in	the	last	
position	in	the	queue.
\end{quote}
\item Public API (\textit{Note: Not really a "domain detail"})
\item \textbf{Part 2:} A user can reserve a taxi by specifying origin and destination.
    A reservation( $ r:O \rightarrow D  $):
    \begin{itemize}
\item \textbf{MUST} occur at least 2 hours before.
\item Is confirmed to the user by the system, which allocates a taxi 10 mins before.
\end{itemize}
\item \textbf{Part 3:} A \textbf{sharing option} must be available, which:
\begin{itemize}
\item It gives the possibility to share the reservation and the costs.
\item It requires the user to specify the destination of all rides it wants to share.
\item The system will find other users in the same zone, calculate the fee and notify the users.
\end{itemize}
\end{itemize}


