	\subsection{UNDER DEVELOPMENT}

	1. Specific Requirements In this section detailed descriptions of the functional and quality requirements will be presented together with explicit features requested.
		a. External Interface RequirementsIn the paragraphs below an analysis of inputs to and outputs from the system will be presented both from the user and software perspectives.
			i. User InterfacesThe first view an user should see is the Sign In page both from mobile and web apps.Then, if it's their first time within the application, the user should move to the sign up page, in order to begin the registration process.
			
			If however they already have an account, after the sign in process:
			
			- If the user is a passenger, they will se the Home page which contains a brief history of previous rides and an option to do a new ride.
			
			- If instead the user is a taxi driver they will directly see the Driver page which shows recent notifications and a map with the route to the next destination.
			- If 
			
			ii. Hardware InterfacesSince the application is compliant to modern standards, there is no specific limitation on the hardware itself. The only limitation to use the app is that it must be used from a GPS enabled device.
			iii. Communication Interfaces
			Since both the front-end and the back-end are being developed from scratch, there are no specific restrictions on the communication between system components except from the underlying data layer which will be discussed later.
