% --------------------------------------------------
% PLEASE REMEMBER TO UPDATE TIME SPENT IN time.tex
% --------------------------------------------------

\section{Introduction}

\subsection{Purpose}
This document has the \textbf{goal} of providing an overall and complete description of \textit{myTaxiService}'s software architectural design together with algorithms and UI.\\
The intended audience of this document are project managers and software developers.

\subsection{Scope}
\textit{myTaxiService} is an application born to support an existing taxi company, especially to simplify passengers' access to the service and guarantee a fair management of taxi queues. In fact it will be GPS-based and it will be able to assign a taxi to a certain call, based on the location of the taxi and of the requesting passenger, in order to minimize the waiting time.\\
It will also provide an option to reserve a taxi in advance and to share the ride with other passengers to save money. All these features will be available via a freely downloadable mobile application or a web application.\\
It will also provide an interface for the taxi drivers, in order to communicate with them more easily and to make them able to automatically share their location over time.

\subsection{Definitions, Acronyms, Abbreviations}

\subsubsection{Definitions}
\begin{itemize}
\item \textbf{Dynamic queue}: it is a list of taxis which is created whenever a request must be managed.
\item \textbf{Static queue}: it is a list of taxis which is associated to every zones. 
\end{itemize}

\subsubsection{Acronyms \& Abbreviations}
\begin{itemize}
\item \textbf{UML}: Unified Modeling Language
\item \textbf{API}: Application Programming Interface
\item \textbf{MVC}: Model - View - Controller
\item \textbf{DTO}: Data Transfer Object
\item \textbf{PSP}: Payment Service Provider
\end{itemize}


\subsection{Document Structure}
The document divides into 5 parts:
\begin{itemize}

\item Section 1: \textbf{Introduction}. It gives a description of the document underlining his goals and gives basic information about the application.

\item Section 2: \textbf{Architectural Design}. It gives the various architectural views of the application.

\item Section 3: \textbf{Algorithm Design}. It gives some algorithms' descriptions contained in the application.

\item Section 4: \textbf{User Interface Design}. It shows application's mockups.

\item Section 5: \textbf{Requirements Traceability}. It contains solutions to the RASD requirements.

\item Section 6: \textbf{References}. It contains all DD's references.

\end{itemize}

